---
title: "Getting Started with GeneralAnalyser"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with GeneralAnalyser}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(GeneralAnalyser)
```

## Introduction

GeneralAnalyser is a comprehensive analytics platform that enables users to perform advanced data analysis through an intuitive interface. This vignette will walk you through the basic usage of the package.

## Data Input

GeneralAnalyser supports multiple data sources:

```{r eval=FALSE}
# Load data from CSV
data <- load_file_data("your_data.csv")

# Connect to database
db_params <- list(
  host = "localhost",
  dbname = "mydb",
  user = "user",
  password = "pass"
)
db_conn <- connect_db(db_params)

# Fetch API data
api_config <- list(
  url = "https://api.example.com/data",
  auth_token = "your_token"
)
api_data <- fetch_api_data(api_config)
```

## Time Series Analysis

Perform time series forecasting:

```{r eval=FALSE}
# Create sample time series data
data <- ts(rnorm(100) + 1:100, frequency = 12)

# Generate forecast
forecast_result <- ts_forecast(data, horizon = 12, method = "auto.arima")
plot(forecast_result)

# Decompose time series
decomp <- ts_decompose(data)
plot(decomp)
```

## Regression Analysis

Fit and evaluate regression models:

```{r eval=FALSE}
# Prepare data
data <- data.frame(
  y = rnorm(100),
  x1 = rnorm(100),
  x2 = rnorm(100)
)

# Fit model
model <- fit_regression(data, "y", c("x1", "x2"), method = "linear")

# Cross-validate
cv_results <- cross_validate(model, data)
print(cv_results)

# Get diagnostics
diagnostics <- regression_diagnostics(model)
```

## Classification

Train and evaluate classifiers:

```{r eval=FALSE}
# Prepare classification data
data <- data.frame(
  x1 = rnorm(100),
  x2 = rnorm(100),
  y = factor(rep(c("A", "B"), each = 50))
)

# Train classifier
model <- train_classifier(data, "y", c("x1", "x2"), method = "rf")

# Evaluate performance
results <- evaluate_classifier(model, data, data$y)
print(results$confusion_matrix)

# Get feature importance
importance <- feature_importance(model, c("x1", "x2"))
```

## Clustering

Perform cluster analysis:

```{r eval=FALSE}
# Prepare clustering data
data <- data.frame(
  x = c(rnorm(50, 0), rnorm(50, 3)),
  y = c(rnorm(50, 0), rnorm(50, 3))
)

# Perform clustering
result <- perform_clustering(data, method = "kmeans", params = list(k = 2))

# Evaluate clustering
metrics <- evaluate_clustering(result)

# Find optimal number of clusters
optimal_k <- find_optimal_k(data, max_k = 10)
```

## Anomaly Detection

Detect anomalies in your data:

```{r eval=FALSE}
# Generate sample data with anomalies
data <- c(rnorm(100), rep(5, 5))

# Detect anomalies
anomalies <- detect_anomalies(data, method = "zscore")

# Generate report
report <- generate_anomaly_report(anomalies, data)
print(report)

# Detect seasonal anomalies
seasonal_data <- ts(data, frequency = 12)
seasonal_anomalies <- detect_seasonal_anomalies(seasonal_data)
```

## Customization

The package supports custom themes and visualizations:

```{r eval=FALSE}
# Initialize custom theme
theme <- initialize_theme(type = "dark")

# Create custom plot theme
plot_theme <- create_plot_theme(base_size = 14)

# Apply custom dashboard theme
dashboard_theme <- create_dashboard_theme(type = "dark")
```

## Conclusion

This vignette covered the basic functionality of GeneralAnalyser. For more advanced usage and detailed documentation, please refer to the function documentation and other vignettes.